Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-16

### 2016-02-19 ec-2016/source/paper.tex
Added most of Attack-Tolerant Network Infrastructure section.

Sparse

Low-diameter

Vertex-transitivity

Redundancy
\cite{baran_distributed_1964}

Routing

>>>>

To achieve scalability, networks must be {\em sparse} and have a
{\em low diameter}.
In practical settings, humans and devices have an upper limit on the number
of connections they can maintain.
In sparse networks, the number of links grows slowly as the network grows in
size, allowing the network to scale without exceeding the nodes' capacity for
links.
Similarly, low-diameter guarantees that as a network grows, a short path will
still exist between any pair of nodes.
While low diameter guarantees a path exists,
paths are only useful if an efficient {\em routing} algorithm exists
to find them.

Redundancy in a network can help reduce single points of failure as well as
increase fault-tolerance.
One measure of redundancy is given by the ratio of edges to nodes
\cite{baran_distributed_1964}.
A single points of failure occur when a node holds a uniquely
central position,
and can be eliminated by adding alternative
paths around the node,
which increases the network's redundancy.
Similarly, redundancy in a network can enable fault-tolerance techniques
that reduce the effectiveness of attacks and creating stabilizing asymmetry.
When secrecy is desired, redundancy can help by allowing messages to be
divided into parts and sent along different paths so even if one path is
compromised, the whole message is not revealed.

Networks with {\em vertex transitivity} have the greatest protection agasint
single points of failure.
In vertex transitive networks, for any pair of nodes, an edge-preserving map
always exists from one node to the other.
In other words, all nodes occupy structurally indistinguishable positions
in the network.
